A 38 Million Year Old Neptune-Sized Planet in the Kepler Field

### 2021-12-07 paper_review/response_1.txt

Dear Dr. Jackson,

We thank you for organizing the review of our paper, and also thank
the referees for constructive criticism.  We have considered the
remarks of both of the reviewers carefully and revised our manuscript
accordingly.

Below, we have reproduced the relevant portions of the reviews' reports,
alongside our responses. The changes are bolded in the  attached
ms_boldchanges.pdf file, using the trackchanges AASTeX macros.

@@

REVIEWER COMMENT
----------
Line 230 (age): Consider adopting a systematic error (perhaps
corresponding to the range noted for the extremes of the ages) in
addition to the random (assumed to be the quoted +6/-5 error).
Relatedly, how are the quoted errors derived?

RESPONSE
----------
> We're comfortable quoting the statistical error derived from the
> standard deviation of the logarithmic age posterior since this
> distribution is roughly Gaussian (see the attached
> del_lyr_cluster_age_posterior.png).  The worry with quoting a
> systematic error, e.g., "The age of the δ Lyr cluster is
> $38^{+6}_{-5}$ (stat) $^{+6}_{-8}$ (sys)" is that the systematic
> uncertainties are not based on any probability distribution that
> we can easily assess -- they're estimated based on the extremes of
> previous literature age measurements.  Quoting this systematic
> range next to a number that has been derived based on a more
> formal approach (and that has statistical meaning within that
> approach) somehow misses this point.  We would prefer to leave the
> discussion in the manuscript as-is in order to communicate the
> spread of ages from different measurement approaches (which
> reflects a systematic uncertainty in the overall age scale),
> rather than quoting separate statistical and systematic
> uncertainties.

@@

REVIEWER COMMENT
----------
Line 235: May be worth mentioning the restriction to the 391 stars in
the beginning of sec 2.2.2.

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
Line 278: "Indistinguishable" -- from each other or from the Pleiades?

RESPONSE
----------
> From each other, and the manuscript has been updated; thank you!

@@

REVIEWER COMMENT
----------
Line 286: I thought I remember Curtis or Douglas citing binarity as a
possibility for stars above to slow sequence as well, but I don't
have a reference on-hand.

RESPONSE
----------
> Thank you for this point -- we've updated the text with a
> reference to Stauffer+16.  In their Section 5.1, they discuss the
> case of some unresolved F+K binaries in the Pleiades which show
> anomalously long K2 rotation periods.

@@

REVIEWER COMMENT
----------
Abstract
line 24: Kepl-1627Ab cannot be a "mini-Neptune" if it is same size of
Neptune.  Replace with "Neptune-size" Yes, it falls within a
distribution of objects in a period-radius diagram with an average
that is smaller than Neptune, but claiming affiliation with smaller
objects implies more than we know about this planet, e.g. its mass.

RESPONSE
----------
> Point well-taken.  R_p = 3.82 +/- 0.16 R_earth, so yes, Kepler-1627
> Ab is the same size as Neptune within 1-sigma.  All instances in
> the text that referred to Kepler-1627 Ab as a mini-Neptune have
> been modified to call it a "Neptune-sized planet", including the
> manuscript's title.

REVIEWER COMMENT
----------
line 25: Kepler target stars were chosen for their suitability for
transiting detection of planets in general, and for planets that are
Earth-analogs in paraticular. That involves radius, brightess.
Distance and spectral types were not direct selection criteria; this
was before Gaia.

RESPONSE
----------
> Thank you for this point.  Batalha+2010 (ApJL) discuss the
> selection function.  The sentence in L25 currently states that
> "The star was observed by the Kepler space telescope because it is
> nearby (d=329pc) and it resembles the Sun".  More directly, yes,
> the star was chosen because it was thought that it might enable
> the detection of small planets in the habitable zone.  However the
> underlying reason for why the star enables such detections is
> based on the star's brightness and assumed radius, which both
> factor into the transit SNR ( SNR ~ δ/σ ~ (Rplanet/Rstar)^2 *
> (1/σ(Kepmag)); for σ(Kepmag) the relative precision as a function
> of Kepler magnitude ).  Our claim therefore holds, albeit
> indirectly: a star of the same color that was too far away would
> not have been selected because it would be too faint.  If it were
> the wrong color, it also wouldn't have been selected.  But perhaps
> we are getting a bit too pedantic: this sentence also serves the
> more important purpose of informing the reader what kind of star
> this paper is about: a star that is at a distance of ~330 parsecs,
> and that resembles the Sun (except for its age!).

@@

REVIEWER COMMENT
----------
Figure 3 bottom: Can the IC 2602 and 2391 rotation periods be added
to this plot? Lines 276-278 mention that these and cite Douglas et
al. 2021 (although the reference does not seem to be complete). Isn't
it interesting that the interlopers all fall on the Praesepe rotation
sequence?

RESPONSE
----------
> Thank you for pointing out the missing link in the reference to
> Douglas et al. 2021, which should have pointed to
> https://ui.adsabs.harvard.edu/abs/2021tsc2.confE.157D/abstract,
> and has been updated in the revision.  The rotation periods from
> this work, which includes IC 2602, IC 2391, and a few other 30-50
> Myr clusters, are not yet public.  
>
> The interlopers falling on the Praesepe sequence is indeed a bit
> odd, but it's really only ~3-5 stars. A much bigger set of
> interlopers didn't have detected rotation periods at all! (See
> final paragraph of Section 2.2.2).  At the other reviewer's
> request, we've also added a sentence noting that some of these
> stars might be unresolved F+K binaries.

@@

REVIEWER COMMENT
----------
p 5 lines 258-261: rather than simply throw the TESS values out in
favor of the Kepler ones, the authors should compare them to evaluate
the accuracy and reliability of the TESS values.

RESPONSE
----------
> Thank you for this point -- please see kepler_vs_tess_prot.png in
> the attached response, which shows the 28 referenced stars that
> overlap.  5 of the 28 stars have Kepler rotation periods above 10
> days, of which none were correctly recovered by TESS (3 are chosen
> at the half-period harmonic).  Of the 23 stars with periods below
> 10 days, 21 of the TESS periods agree with the Kepler rotation
> periods, and 2 are at the double-period harmonic.
>
> We've updated the text to reflect this point, which doesn't affect
> any of the conclusions given that almost all the δ Lyr cluster
> stars have rotation periods below below 10 days.

### 2021-12-07 paper/ms.tex
AAS resubmitted

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2021 Oct 12}
\revised{---}
\accepted{---}
\submitjournal{AAS Journals}
\shorttitle{Kepler\,1627}

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  \replaced{In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}). The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.}{The
pre-main-sequence M dwarfs of the \cn\ were also seen to be ``below''
UCL and ``above'' the Pleiades.}  To turn this heuristic interpolation
into \replaced{an age}{a quantitative age}
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, \replaced{we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively}{we used UCL, IC\,2602, and the
Pleiades}.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the CAMD.\footnote{
  For a description of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note
  \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}.}  We then passed a
moving box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid
of \deleted{hybrid }isochrones spanning the ages between UCL \replaced{to}{and} the Pleiades using
Equation\replaced{s~6 and~7}{~6} from
\citet{gagne_mutau_2020}.  
\added{To derive a probability distribution function for the age of \cn, we
then assumed a Gaussian likelihood that treated the interpolated isochrones as
the ``model'' and the $\delta$\ Lyr\ cluster's isochrone as the ``data''
(Equation~7 from \citealt{gagne_mutau_2020}).  The cluster's age and its
statistical uncertainty are then quoted as the the mean and standard deviation
of this age posterior.}

@@

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.\deleted{ As a
matter of scope, we restricted our attention to the \nkinwithtess\
stars discussed in Section~\ref{sec:kinematicselection} in the spatial
and kinematic proximity of Kepler\,1627.}\deleted{ Kepler rotation
periods were derived by \citet{mcquillan_rotation_2014} for 28 of
our \nkinwithtess\ stars; for these cases, we
simply adopted the Kepler rotation period.}\added{ First, to validate
the TESS rotation periods, we compared against 28 stars
from \citet{mcquillan_rotation_2014} that were also observed by Kepler.  Of the 23 stars with Kepler
periods below 10 days, 21 of the TESS periods agreed with the Kepler
rotation periods; the other 2 were measured at the double-period
harmonic.  Of the remaining 5 stars with Kepler rotation periods above
10 days, none were correctly recovered by TESS, and 3 were near the
half-period harmonic.  We therefore adopted a general stance of
skepticism for TESS rotation periods exceeding 10 days, and used the
Kepler rotation periods whenever possible.}
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large \replaced{renormalized
unit weight error (RUWE),}{RUWE} relative to other members of the \cn\
\added{(RUWE$\approx$2.9; roughly the $98^{\rm th}$ percentile of the cluster's
distribution)}.  Based
on the apparent separation, the binary orbital period is of order
hundreds of years.  The large RUWE is therefore more likely to be
caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the low geometric probability that a companion imaged at $\rho
\approx 0\farcs16$ is a chance line-of-sight companion, we proceed
under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of \replaced{$M_{\rm B} \approx
0.33 M_{\odot}$}{$M_{\rm B} \approx 0.30 M_{\odot}$} and companion
temperature of \replaced{$T_{\rm eff,B} \approx 3450$}{$T_{\rm eff,B}
\approx 3408$} K.  The corresponding spectral type is roughly \replaced{M2.5}{M3}V
\citep{pecaut_mamajek_2013}.  These models combined with the NIRC2
contrast limits imply physical limits on tertiary companions of
$M_{\rm ter} < 50 M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20
M_{\rm Jup}$ at $\rho = 100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$
at $\rho = 330$\,AU.

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope for the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}. \added{The
best-fit line yields $\chi^2 = 306.1$, with $n=140$ data points.  An alternative
model of just a flat line yields $\chi^2=315.6$.  The difference in the
Bayesian information criterion between the two models is ${\rm
BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$,
which corresponds to a Bayes factor of $\approx$9.4. According to the
usual \citet{kass_bayes_1995} criteria, this is ``positive'' evidence
for the model with a finite slope.  We view it as suggestive
at best, particularly given the poor reduced $\chi^2$.}

\replaced{One}{A separate} concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, using the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
a similar anti-correlation in the injected transits as that present in the real
transit;
using this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below. Given the
\added{lack of }statistical significance, this analysis should be interpreted as
suggestive at best.

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge it would be the youngest planet yet found by the
\replaced{main}{prime} Kepler mission.\footnote{The re-purposed K2 mission however has found
two younger systems containing five planets: K2-33b ($9\pm1\,{\rm
Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and V1298 Tau
($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}   Could the transit
be produced by anything other than a planet orbiting this near-solar
analog?  \citet{morton_false_2016} validated the planet based on the
transit shape, arguing that the most probable false positive scenario
was that of a background eclipsing binary, which had a model-dependent
probability of $\approx$$10^{-5}$.  However, this calculation was
performed without knowledge of the low-mass stellar companion ($M_{\rm
B}\approx 0.33\,M_\odot$).  Validated planets have also previously
been refuted \citep[{\it e.g.},][]{shporer_three_2017}.  We therefore
reassessed false positive scenarios in some detail.

@@

As an initial plausibility check, Kepler\,1627B contributes 1\% to 2\%
of the total flux observed in the Kepler aperture.  For the sake of
argument, assume the former value.  The observed transit has a depth
of $\approx$0.18\%.  A 18\% deep eclipse of Kepler\,1627B would
therefore be needed to produce a signal with the appropriate depth.
The shape of the transit signal however requires the impact parameter
to be below 0.77 (2-$\sigma$); the tertiary transiting the secondary
would therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
This yields a contradiction:  this scenario requires an ingress
and egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm min}$).  The actual measured ingress and egress
duration is $\approx 17\,{\rm min}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

% Baraffe+15: M_B 0.33 Mdot
% Rstar = 0.455 --> 0.465 Rsun

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B \added{given its
nominal age of 38\,Myr and mass of 0.30\,$M_\odot$} is $\approx 4.6\,{\rm
g\,cm}^{-3}$ \citep{baraffe_new_2015}.
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.\added{ Adversarially assuming a younger age (32\,Myr) and a larger companion
mass (0.35\,$M_\odot$), the companion's density could be as low as $\approx 3.5\,{\rm
g\,cm}^{-3}$.  This is still in tension with the data.} While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the \cn\ locus on the Gaia CAMD (Figure~\ref{fig:age}).

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019}, HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.  \replaced{However,}{However, it seems that} smaller planets could have been
detected: \added{based on the per-target detection contours, }the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days
\citep{2021ascl.soft07027B}.
\added{These limits account for the spot-induced variability in the
system through
a correction based on the Combined Differential Photometric Precision
in the \sn\ light curve over the relevant transit timescales
\citep{2017ksci.rept...19B}.} The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$\deleted{ to 10$\,M_\oplus$} mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  
\added{
It could also be consistent with a scenario in which an earlier ``boil-off'' of
the planet's atmosphere during disk dispersal decreases the entropy of
the planetary interior, leading to a $\sim$10$^8$ year Kelvin-Helmholtz
contraction timescale
\citep{owen_constraining_2020}.
Confirming either of these scenarios would require a measurement
of the planetary mass; otherwise, alternative explanations for its large size
could include that it is abnormally massive, or that it has an abnormally
large envelope to core mass ratio.}

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2021 Oct 12}
\revised{2021 Dec 6}
\accepted{---}
\submitjournal{AAS Journals}
\shorttitle{Kepler\,1627}

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and
therefore are approximately the same age.  \replaced{In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}). The
pre-main-sequence M dwarfs of the \cn\ were intermediate between the
latter two clusters.}{The
pre-main-sequence M dwarfs of a fixed color in the \cn\ are more luminous than those of the Pleiades, and were also seen to be 
less luminous than those in
UCL.}  To turn this heuristic interpolation
into \replaced{an age}{a quantitative age}
measurement, we used the empirical method developed by
\citet{gagne_mutau_2020}.  In brief, we fitted the pre-main-sequence
loci of a set of reference clusters, and the locus of the target \cn\
was then modeled as a piecewise linear combination of these reference
clusters.  For our reference clusters, \replaced{we adopted members of UCL,
IC\,2602, and the Pleiades from \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively}{we used UCL, IC\,2602, and the
Pleiades}.  We removed binaries by
requiring $\texttt{RUWE}<1.3$, $\texttt{radial\_velocity\_error}$
below the 80$^{\rm th}$ percentile of each cluster's distribution, and
excluded stars that were obvious photometric binaries in the CAMD.\footnote{
  For a description of the renormalized unit weight error (RUWE), see the GAIA DPAC technical note
  \url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}.}  We then passed a
moving box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid
of \deleted{hybrid }isochrones spanning the ages between UCL \replaced{to}{and} the Pleiades using
Equation\replaced{s~6 and~7}{~6} from
\citet{gagne_mutau_2020}.  
\added{To derive a probability distribution function for the age of \cn, we
then assumed a Gaussian likelihood that treated the interpolated isochrones as
the ``model'' and the $\delta$\ Lyr\ cluster's isochrone as the ``data''
(Equation~7 from \citealt{gagne_mutau_2020}).  The cluster's age and its
statistical uncertainty are then quoted as the the mean and standard deviation
of this age posterior.}

@@

We then cleaned the candidate TESS rotation period measurements
through a combination of automated and manual steps.\deleted{ As a
matter of scope, we restricted our attention to the \nkinwithtess\
stars discussed in Section~\ref{sec:kinematicselection} in the spatial
and kinematic proximity of Kepler\,1627.}\deleted{ Kepler rotation
periods were derived by \citet{mcquillan_rotation_2014} for 28 of
our \nkinwithtess\ stars; for these cases, we
simply adopted the Kepler rotation period.}\added{ First, to validate
the TESS rotation periods, we compared against 28 stars
from \citet{mcquillan_rotation_2014} that were also observed by Kepler.  Of the 23 stars with Kepler
periods below 10 days, 21 of the TESS periods agreed with the Kepler
rotation periods; the other 2 were measured at the double-period
harmonic.  Of the remaining 5 stars with Kepler rotation periods above
10 days, none were correctly recovered by TESS, and 3 were near the
half-period harmonic.  We were therefore 
wary of any TESS rotation periods exceeding 10 days, and used the
Kepler rotation periods whenever possible.}
For the remaining stars with only TESS data, we
focused only on the stars for which no companions were known with a brightness
exceeding one-tenth of the target star in a $21\farcs0$ radius.  There
were \nkinwithtessandcrowding\ stars that met these crowding requirements, and
that had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself: we required the
Lomb Scargle power to exceed 0.2, and the period to be below 15\,days.

@@

% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no comoving, codistant candidate companions
brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its
existence was also suggested by the primary star's large \replaced{renormalized
unit weight error (RUWE),}{RUWE} relative to other members of the \cn\
\added{(RUWE$\approx$2.9; roughly the $98^{\rm th}$ percentile of the cluster's
distribution)}.  Based
on the apparent separation, the binary orbital period is of order
hundreds of years.  The large RUWE is therefore more likely to be
caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the low geometric probability that a companion imaged at $\rho
\approx 0\farcs16$ is a chance line-of-sight companion, we proceed
under the assumption that the companion is bound, and that
Kepler\,1627 is a binary.  Given the distance and age, the models of
\citet{baraffe_new_2015} imply a companion mass of \replaced{$M_{\rm B} \approx
0.33 M_{\odot}$}{$M_{\rm B} \approx 0.30\,M_{\odot}$} and companion
temperature of \replaced{$T_{\rm eff,B} \approx 3450$}{$T_{\rm eff,B}
\approx 3408$}\,K.  The corresponding spectral type is roughly \replaced{M2.5}{M3}V
\citep{pecaut_mamajek_2013}.  These models combined with the NIRC2
contrast limits imply physical limits on tertiary companions of
$M_{\rm ter} < 50 M_{\rm Jup}$ at $\rho = 50$\,AU, $M_{\rm ter} < 20
M_{\rm Jup}$ at $\rho = 100$\,AU, and $M_{\rm ter} < 10 M_{\rm Jup}$
at $\rho = 330$\,AU.

@@

We therefore isolated each of the 144 observed transits to within
$\pm4.5$\,hr of each transit, and fitted each window with both {\it
i)} a local \added{second or fourth-order }polynomial baseline plus the transit, and {\it ii)} a local linear
trend\added{ plus the transit}.  \deleted{We considered the results both for a second and fourth-order
time-dependence in the local baseline.  }We let the mid-time of each
transit float, and then calculated the residual between the measured
mid-time and that of a periodic orbit.  This residual, the transit
timing variation, is plotted in Figure~\ref{fig:corr} against
the local linear slope \replaced{for}{assuming} the fourth-order polynomial baseline.  The
slope of $-21 \pm 10\,{\rm min\,day}^{-1}$ is similar to that
found by \citet{holczer_time_2015}. \added{The
best-fit line yields $\chi^2 = 306.1$, with $n=140$ data points.  An alternative
model of just a flat line yields $\chi^2=315.6$.  The difference in the
Bayesian information criterion between the two models is ${\rm
BIC}_{\rm flat} - {\rm BIC}_{\rm line} = 4.5$,
which corresponds to a Bayes factor of $\approx$9.4. According to the
usual \citet{kass_bayes_1995} criteria, this is ``positive'' evidence
for the model with a finite slope.  We view it as suggestive
at best, particularly given the poor reduced $\chi^2$.}

\replaced{One}{A separate} concern we had in this analysis was whether our transit fitting
procedure might induce spurious correlations between the slope and
transit time.  In particular, assuming the second-order polynomial
baseline yielded a larger anti-correlation between the TTVs and local
slopes, of $-79 \pm 14\,{\rm min\,day}^{-1}$.  We therefore
performed an injection-recovery procedure in which we injected
transits at different phases in the \sn\ light curve and repeated the
TTV analysis.  This was done at $\approx$50 phases, each separated by
$0.02\,P_{\rm orb}$ while omitting the phases in transit.  For
the second-order polynomial baseline, this procedure yielded
a similar anti-correlation in the injected transits as that present in the real
transit;
assuming this baseline would therefore bias the
result.  However for the fourth-order baseline, the correlation
present in the data was stronger than in all but one of the injected
transits.
Possible interpretations are discussed below. Given the
\added{lack of }statistical significance, this analysis should be interpreted as
suggestive at best.

@@

If the \pn\ transit signal is created by a genuine planet,  then to
our knowledge it would be the youngest planet yet found by the
\replaced{main}{prime} Kepler mission.\footnote{The re-purposed K2 mission however has found
two younger systems containing five planets: K2-33b ($9\pm1\,{\rm
Myr}$; \citealt{Mann_K2_33b_2016,David_et_al_2017}) and V1298 Tau
($23\pm4\,{\rm Myr}$; \citealt{david_four_2019}).}   Could the transit
be produced by anything other than a planet orbiting this near-solar
analog?  \citet{morton_false_2016} validated the planet based on the
transit shape, arguing that the most probable false positive scenario
was that of a background eclipsing binary, which had a model-dependent
probability of $\approx$$10^{-5}$.  However, this calculation was
performed without knowledge of the low-mass stellar companion ($M_{\rm
B}\approx 0.30\,M_\odot$).  Validated planets have also previously
been refuted \citep[{\it e.g.},][]{shporer_three_2017}.  We therefore
reassessed false positive scenarios in some detail.

@@

As an initial plausibility check, Kepler\,1627B contributes 1\% to 2\%
of the total flux observed in the Kepler aperture.  For the sake of
argument, assume the former value.  The observed transit has a depth
of $\approx$0.18\%.  An $\approx$18\% deep eclipse of Kepler\,1627B would
therefore be needed to produce a signal with the appropriate depth.
The shape of the transit signal however requires the impact parameter
to be below 0.77 (2-$\sigma$); the tertiary transiting the secondary
would therefore need to be non-grazing with $R_3/R_2 \approx 0.4$.
This yields a contradiction:  this scenario requires an ingress
and egress phase that each span $\approx$40\% of the transit duration
($\approx 68\,{\rm min}$).  The actual measured ingress and egress
duration is $\approx$$17\,{\rm min}$, a factor of four times too
short.  The combination of Kepler 1627B's brightness, the transit
depth, and the ingress duration therefore disfavor the scenario that
Kepler 1627B might host the transit signal.

Beyond this simple test, a line of evidence that
effectively confirms the planetary interpretation is that the stellar density
implied by the transit duration and orbital period is inconsistent
with an eclipsing body around the M-dwarf companion.  We find
$\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for Kepler\,1627B \added{given its
nominal age of 38\,Myr and mass of 0.30\,$M_\odot$} is $\approx$$4.6\,{\rm
g\,cm}^{-3}$ \citep{baraffe_new_2015}.
The transit duration is therefore too long to be explained by a star
eclipsing the M dwarf secondary at $10$-$\sigma$.\added{ Adversarially assuming a younger age (32\,Myr) and a larger companion
mass (0.35\,$M_\odot$), the companion's density could be as low as $\approx 3.5\,{\rm
g\,cm}^{-3}$.  This is still in tension with the fitted stellar density.} While the planet
might hypothetically still orbit a hidden close and bright companion,
this possibility is implausible given {\it i)} the lack of secondary
lines in the HIRES spectra, {\it ii)} the lack of secondary
rotation signals in the Kepler photometry, and {\it iii)} the proximity
of \sn\ to the \cn\ locus on the Gaia CAMD (Figure~\ref{fig:age}).

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019}, HIP~67522
\citep{rizzuto_tess_2020}, TOI~837 \citep{bouma_cluster_2020}, the
two-planet AU~Mic \citep{plavchan_planet_2020,martioli_aumicbc_2021}
and the four-planet V1298~Tau \citep{david_four_2019}.  \pn\ is one of
the smaller planets in this sample ($3.82\pm0.16\,R_\oplus$), which
could be linked to the selection effects imposed by spot-induced
photometric variability at very young ages \citep[{\it
e.g.},][]{zhou_2021_tois}.

 \replaced{However,}{It seems though that} smaller planets could have been
detected\added{ in the \sn\ system}: \added{based on the per-target detection contours, }the Kepler pipeline's median completeness extended to
$1.6\,R_\oplus$ at 10~day orbital periods, and $3.3\,R_\oplus$ at
100~days
\citep{2021ascl.soft07027B}.
\added{These limits account for the spot-induced variability in the
system through
a correction based on the Combined Differential Photometric Precision
in the light curve over the relevant transit timescales
\citep{2017ksci.rept...19B}.} The large size of \pn\ relative
to most Kepler mini-Neptunes might therefore support a picture
in which the typical $5\,M_\oplus$\deleted{ to 10$\,M_\oplus$} mini-Neptune
\citep{wu_mass_2019} loses a significant fraction of its primordial
atmosphere over its first gigayear
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  
\added{
It could also be consistent with a scenario in which an earlier ``boil-off'' of
the planet's atmosphere during disk dispersal decreases the entropy of
the planetary interior, leading to a rather long $\sim$10$^8$ year Kelvin-Helmholtz
contraction timescale
\citep{owen_constraining_2020}.
Confirming either of these scenarios would require a measurement
of the planetary mass; otherwise, alternative explanations for its large size
could include that it is just abnormally massive, or that it has an abnormally
large envelope to core mass ratio.}
